### 2021-06-18 results.tex
update all paper and response letter
Results and setup

Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. Besides that, in the first execution (WS), none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
At this point, an additional question arises: what are the characteristics
of the malwares that have (not) been identified using the mining sandbox approach?
To explore this question, we take advantage of the
\texttt{dex2jar} tool to reverse-engineer all 96 malwares considered in our analysis and
computed the \emph{diffs} of the benign/malicious versions of the APPs.
The results of this activity are available in our replication
package.\footnote{https://github.com/droidxp/paper-replication-package/blob/master/diff/} 
In what follows we dissect a few examples of malwares
that at least one dynamic analysis tool was able to
identify using the mining sandbox approach. After that,
we present the characteristics of a malware that none of the tools
was able to detect. Our goal here is to provide
a lower-level intuition about the classes of malware the
mining sandbox approach is able to detect. A reader that
is not interested in these details could skip to
Section~\ref{sec:res-ss}.

@@

In this second study we used a taint analysis approach to mine differences between the
benign and malicious versions of the 96 Android apps in our dataset. To this end we leverage the FlowDroid
%\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
tool, which tracks how sensitive information flows through the apps using taint analysis algorithms.
Regarding accuracy, the taint analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%). That is,
using the taint analysis implementation of FlowDroid alone outperforms the Monkey, DroidMate,
and Humanoid sandboxes computed in the second execution (without the DroidFax static analysis
algorithms). This result shows that static analysis algorithms are promising for mining
sandboxes, demystifying previous claims in the literature.

>>>>

Altogether, ignoring  \joke, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. Besides that, in the first execution (WS), none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
At this point, an additional question arises: what are the characteristics
of the malwares that have (not) been identified using the mining sandbox approach?
To explore this question, we take advantage of the
\texttt{dex2jar} tool to reverse-engineer all 96 malwares considered in our analysis and
computed the \emph{diffs} of the benign/malicious versions of the APPs.
The results of this activity are available in our replication
package.\footnote{https://github.com/droidxp/paper-replication-package/blob/master/diff/} 
In what follows we dissect a few examples of malwares
that at least one dynamic analysis tool was able to
identify using the mining sandbox approach. After that,
we present the characteristics of a malware that none of the tools
was able to detect. Our goal here is to provide
a lower-level intuition about the classes of malware the
mining sandbox approach is able to detect. A reader that
is not interested in these details could skip to
Section~\ref{sec:res-ss}.

@@

In this second study we used a taint analysis approach to mine differences between the
benign and malicious versions of the 96 Android apps in our dataset. To this end we leverage the FlowDroid
%\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
tool, which tracks how sensitive information flows through the apps using taint analysis algorithms.
Regarding accuracy, the taint analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%). That is,
using the taint analysis implementation of FlowDroid alone outperforms the Monkey, DroidMate,
and Humanoid sandboxes computed in the second execution (without the DroidFax static analysis
algorithms). This result shows that static analysis algorithms are promising to complement mining
sandboxes, demystifying previous claims in the literature.

### 2021-06-18 setup.tex
Results and setup

Our research work aims to better understand
the use of static analysis to mine Android sandboxes
and explore the benefits of combining taint analysis
with the mine sandbox approach for identifying malicious
behavior. 
On the one hand, Jamrozik et al. suggest that a 
static analysis approach for mining sandboxes
might be ineffective---due to \emph{overapproximation
problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
However, to the best of our knowledge,
there is no empirical study comparing
static and dynamic analysis for mining sandboxes.
On the other hand, the \blls explored the mining sandbox approach by comparing
the performance of {\bf dynamic analysis tools} for identifying
malicious behavior. Nonetheless, their
research also involved an external static analysis component (DroidFax)
whose impact on the results was not measured.
This lack of understanding about the implications of
static analysis for mining sandboxes motivates
our research, which investigates the following research questions.

@@

 \item What is the effective performance of each test generation tool, in terms of the number of detected malware, when we
   discard the contributions of the DroidFax static analysis algorithms?

@@

We used DroidXP to systematically assess and compare the
performance of test generation tools for mining android sandboxes. DroidXP relies on a
simple \emph{Command Line Interface} (CLI) that simplifies the integration
of different test generation tools and favors the setup and execution 
of the experiments. DroidXP also relies on DroidFax, which instruments
Android apps and collects relevant information about
their execution, including the set of sensitive APIs a given
app calls during a test execution. DroidFax also collects
inter-component communication (ICC) using  static
program analysis.

>>>>

\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis. a.k.a effect of taint analysis on sandboxes. But in the introduction we kind of use the general S-D interaction and this problem interchangeably. I have left a comment at the introduction.}
Our research work aims to better understand
the use of static analysis to mine Android sandboxes
and explore the benefits of combining taint analysis
with the mine sandbox approach for identifying malicious
behavior. 
On the one hand, Jamrozik et al. suggest that a 
static analysis approach for mining sandboxes
might be ineffective---due to \emph{overapproximation
problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
However, to the best of our knowledge,
there is no empirical study comparing
static and dynamic analysis for mining sandboxes.
On the other hand, the \blls explored the mining sandbox approach by comparing
the performance of {\bf dynamic analysis tools} for identifying
malicious behavior. Nonetheless, their
research also involved an external static analysis component (DroidFax)
whose impact on the results was not measured.
This lack of understanding about the implications of
static analysis for mining sandboxes motivates
our research, which investigates the following research questions.

@@

 \item What is the effective performance of each test generation tool\kn{Should we use the term sandboxes instead of test generation tools? Test generation is just part of sandboxes right?}, in terms of the number of detected malware, when we
   discard the contributions of the DroidFax static analysis algorithms?

@@

\kn{Isnt DroidXP a contribution of our approach? If yes, we should start more confidently than saying we "used" it. We should introduce it as a contribution as such.}
We used DroidXP to systematically assess and compare the
performance of test generation tools for mining android sandboxes. DroidXP relies on a
simple \emph{Command Line Interface} (CLI) that simplifies the integration
of different test generation tools and favors the setup and execution 
of the experiments. DroidXP also relies on DroidFax, which instruments
Android apps and collects relevant information about
their execution, including the set of sensitive APIs a given
app calls during a test execution. DroidFax also collects
inter-component communication (ICC) using  static
program analysis.
